### 2014-03-07 src/intro.Rnw
update
intro

% 1. Describe the problem
% 2. State your contributions
Mutation analysis is a method of evaluation of quality of test-suites. It involves generation
of first (and higher) order mutants, and evaluating the effectiveness of test-suites against
the generated mutants~\cite{lipton1971fault, ammann2008introduction}.
Previous research~\cite{andrews2005mutation} has shown that mutations thus introduced behave
similar to the real-faults.

A major impediment on the path to wide adoption of mutation analysis is its high cost of
execution. A full mutation analysis requires running the test-suite against all the first
order syntactical variants, and is prohibitive for even moderately large programs.

A major strain of research into cost-reduction of mutation analysis is to choose a smaller
representative set of mutants~\cite{offutt2001mutation,jia2011analysis}, often called the
``do fewer'' approach. A major variant of this approach is the selective mutation strategy
which advocates selecting a representative subset of operators based on heuristics and
statistical analysis, and using them instead of the whole gamut of mutation
operators~\cite{offutt1993anexperimental,untch2009onreduced}.

Another fertile area of research has been sampling strategies, where, a smaller representative
sample is used in lieu.
This was investigated first by Acreed~\cite{acree1980mutation} and Budd~\cite{budd1980mutation},
who proposed using only $x$\% of the mutants produced. The studies by Wong and
Mathur, found that random sampling with ratio as low as 10\% could provide
accurate results~\cite{jia2011analysis}.

@@

Finally, clustering of mutants~\cite{hussain08mutation} based on similar test cases has also
been used successfully for mutant reduction. These are explained more in depth in Section~\ref{sec:related}

@@

Our contributions in this paper are the following. First, as described in Section~\ref{sec:methodology},
we seek to improve the statistical confidence in our results by utilizing a much larger sample of projects
(188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
generated test-suites using Randoop~\cite{randoop}. Second, as detailed in Section~\ref{sec:analysis}, we
compare the reduction effectiveness of a large number of random sampling criterias (some of which are novel,
and some that has been proposed by other researchers), and a some of the common operator selection
criterias proposed in literature using statistical analysis. This provides us with insight for choosing
mutation reduction techniqus according to the trade-offs in accuracy, and reduction ratios that a tester
is willing to make for their specific requirements. This is detailed in Section~\ref{sec:results}.

Our conclusion and recommendation for practicing testers are provided in Section~\ref{sec:conclusion}.

% \begin{comment}
%   These approach relies on the fact that some of the mutagens generate a large number of variants, and hence produce highly redundant test cases. Previous research suggested that elimination of mutagens with high fertility results in the reduction of total number of mutations produced, and hence reduces the computational requirements.
%
%   % TODO check the survey again on selective mutation.
%
%   It was recently questioned whether this approach indeed resulted in a tangible improvement over random selection of mutants\cite{zhang2010operator}, which did not find operator based selection to be better than random selection.
%
%
%   Another research, initially by Unch\cite{untch2009onreduced} and recently by Deng et al.\cite{deng2013empirical} suggests using software deletion operator since it produces the least number of mutants (smallest neighborhood). The researchers were able to obtain a close approximation of original mutant score with significant savings with this approach.
%
%   However, our previous research suggests that mutation coverage is closely predicted by statement coverage, this suggests that any criteria that forces accounting of the impact of each statement should provide a close approximation to the full mutation score. Hence, our research suggests that SDL works because it forces accounting of each line, and a random sampling criteria that provides the same criteria should result in similar results.
%
%   In our analysis, we find that a random sampling approach that randomly chose a single mutant per line was found to have a better correlation with the full mutation score than that obtained by SDL. Further it was also found that the mutation score produced by random sampling was closer to the full mutation score than that produced by SDL.
%
% Order of most fertile operators for N-selective operator selection.
% NON_VOID_METHOD_CALLS
% NEGATE_CONDITIONALS
% REMOVE_CONDITIONALS
% DELETE_CONDITIONALS
% RETURN_VALS
% INLINE_CONSTS
% CONSTRUCTOR_CALLS
% EXPERIMENTAL_MEMBER_VARIABLE
% VOID_METHOD_CALLS
% MATH
% CONDITIONALS_BOUNDARY
% INCREMENTS
% REMOVE_INCREMENTS
% RMSWITCH
% EXPERIMENTAL_SWITCH
% INVERT_NEGS
%
% \end{comment}
%
%

>>>>

% 1. Describe the problem
% 2. State your contributions
Mutation analysis is a method of evaluation of quality of test-suites. It involves generation
of  mutants by making syntactic changes to the program. First (higher) order mutants
have one (more) syntactic distance to the origianl program.
Mutants are used to evaluate the effectiveness of test-suites 
~\cite{lipton1971fault, ammann2008introduction}.
Studies like ~\cite{andrews2005mutation} have shown that mutation score 
are predictors of the real fault detection of a test suits.

A major impediment to wider adoption of mutation analysis is its high computational cost.
Set of first oder mutants of a moderate size program can be very large, 
which renders mutation analysis of a test-suite against all the first
order mutants prohibitively time-consuming.

A major strain of research into cost-reduction of mutation analysis is to choose a smaller
representative set of mutants~\cite{offutt2001mutation,jia2011analysis}-- often called the
``do fewer'' approach. This approach can be generally divided into 
selective strategies and sampling strategies.

Selective mutation strategies attempt to select a representative subset of operators based 
on heuristics and statistical analysis. They suggest applying these subsets instead of the 
applying the whole gamut of mutation operators~\cite{offutt1993anexperimental,untch2009onreduced}.

Sampling strategies seek to randomly select smaller representative mutants.
This was investigated first by Acreed~\cite{acree1980mutation} and Budd~\cite{budd1980mutation},
who proposed using only $x$\% of the mutants produced. The studies by Wong and
Mathur, found that random sampling with ratio as low as 10\% could provide
accurate results~\cite{jia2011analysis}.

@@

% {Amin: I am not a fan of this ~\cite{hussain08mutation} }
%Finally, clustering of mutants~\cite{hussain08mutation} based on similar test cases has also
%been used successfully for mutant reduction. These are explained more in depth in Section~\ref{sec:related}

@@

\noindent\textbf{Contribution.} Contributions of this paper are he following.
\begin{itemize}
\item It compares a large number of various mutation sampling and selection strategies (Section~\ref{sec:analysis}).
\item It seek sto improve the statistical confidence in our results by utilizing a much larger sample of projects
      (188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
      generated test-suites using Randoop~\cite{randoop} (Section~\ref{sec:methodology}). 
\item It analyses the results and suggest strategies (Section~\ref{sec:results}).
\end{itemize}

%Our contributions in this paper are the following. First, as described in Section~\ref{sec:methodo%logy},
%we seek to improve the statistical confidence in our results by utilizing a much larger sample of projects
%(188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
%generated test-suites using Randoop~\cite{randoop}. Second, as detailed in Section~\ref{sec:analysis}, we
%compare the reduction effectiveness of a large number of random sampling criterias (some of which are novel,
%and some that has been proposed by other researchers), and a some of the common operator selection
%criterias proposed in literature using statistical analysis. This provides us with insight for choosing
%mutation reduction techniqus according to the trade-offs in accuracy, and reduction ratios that a tester
%is willing to make for their specific requirements. This is detailed in Section~\ref{sec:results}.

%Our conclusion and recommendation for practicing testers are provided in Section~\ref{sec:conclusion}.

% \begin{comment}
%   These approach relies on the fact that some of the mutagens generate a large number of variants, and hence produce highly redundant test cases. Previous research suggested that elimination of mutagens with high fertility results in the reduction of total number of mutations produced, and hence reduces the computational requirements.
%
%   % TODO check the survey again on selective mutation.
%
%   It was recently questioned whether this approach indeed resulted in a tangible improvement over random selection of mutants\cite{zhang2010operator}, which did not find operator based selection to be better than random selection.
%
%
%   Another research, initially by Unch\cite{untch2009onreduced} and recently by Deng et al.\cite{deng2013empirical} suggests using software deletion operator since it produces the least number of mutants (smallest neighborhood). The researchers were able to obtain a close approximation of original mutant score with significant savings with this approach.
%
%   However, our previous research suggests that mutation coverage is closely predicted by statement coverage, this suggests that any criteria that forces accounting of the impact of each statement should provide a close approximation to the full mutation score. Hence, our research suggests that SDL works because it forces accounting of each line, and a random sampling criteria that provides the same criteria should result in similar results.
%
%   In our analysis, we find that a random sampling approach that randomly chose a single mutant per line was found to have a better correlation with the full mutation score than that obtained by SDL. Further it was also found that the mutation score produced by random sampling was closer to the full mutation score than that produced by SDL.
%
% Order of most fertile operators for N-selective operator selection.
% NON_VOID_METHOD_CALLS
% NEGATE_CONDITIONALS
% REMOVE_CONDITIONALS
% DELETE_CONDITIONALS
% RETURN_VALS
% INLINE_CONSTS
% CONSTRUCTOR_CALLS
% EXPERIMENTAL_MEMBER_VARIABLE
% VOID_METHOD_CALLS
% MATH
% CONDITIONALS_BOUNDARY
% INCREMENTS
% REMOVE_INCREMENTS
% RMSWITCH
% EXPERIMENTAL_SWITCH
% INVERT_NEGS
%
% \end{comment}
%
%
% NON_VOID_METHOD_CALLS VOID_METHOD_CALLS CONSTRUCTOR_CALLS
% NEGATE_CONDITIONALS REMOVE_CONDITIONALS DELETE_CONDITIONALS CONDITIONALS_BOUNDARY
% RETURN_VALS INLINE_CONSTS EXPERIMENTAL_MEMBER_VARIABLE
% MATH INCREMENTS REMOVE_INCREMENTS INVERT_NEGS
% RMSWITCH EXPERIMENTAL_SWITCH
